paper_replication

### 2021-12-15 paper_replication.Rmd
Update paper_replication.Rmd

countycentroids <- countycentroids %>% rename(county = COUNAME, state = STNAME)
countycentroids$county <- str_to_title(countycentroids$county)
countycentroids <- countycentroids %>% select(county, state, distancetoprovider)
countycentroids <- countycentroids %>% filter(state != "Puerto Rico")
countycentroids$county <- gsub(countycentroids$county, pattern = " City", replacement = "")

>>>>

countycentroids <- countycentroids %>% rename(county = COUNAME, state = STNAME)
countycentroids$county <- str_to_title(countycentroids$county)
countycentroids <- countycentroids %>% dplyr::select(county, state, distancetoprovider)
countycentroids <- countycentroids %>% filter(state != "Puerto Rico")
countycentroids$county <- gsub(countycentroids$county, pattern = " City", replacement = "")
